R Markdown for Reproducible Research

### 2019-01-06 paper.Rmd
add intro and resources

@@

@@

@@

>>>>

The researcher's task is to uncover new things; challenge conventional wisdom;
explore uncharted territory; and confirm or dismiss bias with facts. In order to
accomplish such feats, it is important that a researcher's results be
_reproducible,_ that is:

> Results are reproducible if they can be reliably replicated or recomputed in
another time or place.

For a researcher that is trying to have an impact that extends beyond the "here and now,"
reproducible results ensure that conclusions are valid in another time and place. Further,
for industries like the Pharmaceutical Industry, reproducibility can be a mandate and 
legal requirement for valid results. As a result, tools like R Markdown that help ensure
reproducible results are valuable tools in a researcher's toolkit.

@@

The story of R Markdown begins with Markdown, a markup language and formatting
syntax designed to be:

 - human readable
 - flexible in its output

For example, where HTML would allow writing bold and italicized text like:

```
This is <b>bold</b> and <i>italicized</i> text
```

Markdown allows bold and italicized text with:

```
This is **bold** and _italicizied_ text
```

A subtle difference, but Markdown is more readable because there are not any
letters injected, and it is _much faster_ to type. It also has more simplicity
in its objectives and flexibility in its output, so where HTML is rendered
almost exclusively in browsers, Markdown can be relevant for the web, print, and
even computer terminals.

@@

If Markdown is a lightweight markup language and text formatting syntax, R Markdown
must be Markdown + R code, right? Yes, with a catch. R Markdown actually supports
_many_ programming languages and output types. It got its start with R, and R is
the primary language engine, but R is an interface language. This means that R
is commonly used to "wrap" or

@@

### Resources

- https://rpubs.com/marschmi/105639
- http://ropensci.github.io/reproducibility-guide/sections/tools/
- http://shop.oreilly.com/product/0636920051435.do
- https://rviews.rstudio.com/2017/03/15/why-i-love-r-notebooks/
- https://rviews.rstudio.com/2018/11/01/r-markdown-a-better-approach/
- https://rviews.rstudio.com/2017/01/25/r-markdown-for-the-enterprise/
- https://rviews.rstudio.com/2018/01/18/package-management-for-reproducible-r-code/
- https://en.wikipedia.org/wiki/Markdown
- https://www.oreilly.com/library/view/the-art-of/9781593273842/ch15.html
